OA Share

### 2020-12-17 analysis/006_license.Rmd
update license

```{r}
p <- cowplot::plot_grid(
  p_1, p_2,
  labels = "AUTO", ncol = 1
)
ggsave(here::here("figure", "license_portfolio.png"), p, dpi = 300, width = 6, height = 6)
```

>>>>

```{r}
p <- cowplot::plot_grid(
  p_2, p_1,
  labels = "AUTO", ncol = 1
)
ggsave(here::here("figure", "license_portfolio.png"), p, dpi = 300, width = 6, height = 6)
```
